Molecular dynamics simulation of synchronization in driven particles

### 2021-02-28 manuscript/manuscript_ajp_2020.tex
fixed terrible sentence #2 in abstract

\begin{abstract}
  Synchronization
  plays a key role in many physical processes.
  %Modeling
  A particle may
  execute
  motion 
  coordinated  with position,
  a synchronization behavior
  that 
  can be used to isolate
  complex natural behaviors,  %to
  either with
  simulations or table-top experiments.
  %provide insight
  We discuss a %simple
  %numerical model %that
  molecular dynamics simulation
  of a single particle
  moving through
  a viscous liquid
  driven 
  across a washboard potential energy landscape.
  Our results show many dynamical patterns
  as we alter the landscape and driving force.
  Under certain conditions,
  the particle velocity and location
  are synchronized or 
  phase-locked,
  forming closed orbits in phase space.
  Quasi-periodic motion is common, % in this system,
  where the
  dynamical center of motion shifts the
  phase space orbit.
  We include molecular dynamics code %and exercises
  to simulate and characterize
  particle dynamics.
  %including 
  %plotting  particle velocity as a function of applied driving force 
  %and phase diagrams of position versus velocity.
  %We demonstrate how to 
  %visualize
  %the system with
  %numerical representations of the landscape
  %and
  %animations of the particle motion.
  %We include sample code
  %and exercises for students
  %with 
  %opportunities
  %to reproduce our results and propose
  %new numerical experiments.
  %With only a few particles in two-dimensions,
  %the simulation runs quickly,
  %making this an appropriate model for undergraduates to explore.  
\end{abstract}
% AJP requires an abstract for all regular article submissions.
% Abstracts are optional for submissions to the "Notes and Discussions" section.

>>>>

\begin{abstract}
  Synchronization
  plays a key role in many physical processes.
  We discuss a %simple
  %numerical model %that
  molecular dynamics simulation
  of a single particle
  moving through
  a viscous liquid
  driven 
  across a washboard potential energy landscape.
  %Modeling
  The particle may move with velocity coordinated 
  to position in the landscape.
  This synchronized motion %ation behavior
  is
  commonly observed in 
  simulations and table-top experiments,
  and
  can be used to isolate
  complex natural behaviors.  
  %provide insight
  Our results show many dynamical patterns
  as we alter the landscape and driving force.
  Under certain conditions,
  the particle velocity and location
  are synchronized or 
  phase-locked,
  forming closed orbits in phase space.
  Quasi-periodic motion is common, % in this system,
  where the
  dynamical center of motion shifts the
  phase space orbit.
  We include molecular dynamics code %and exercises
  to simulate and characterize
  particle dynamics.
  %including 
  %plotting  particle velocity as a function of applied driving force 
  %and phase diagrams of position versus velocity.
  %We demonstrate how to 
  %visualize
  %the system with
  %numerical representations of the landscape
  %and
  %animations of the particle motion.
  %We include sample code
  %and exercises for students
  %with 
  %opportunities
  %to reproduce our results and propose
  %new numerical experiments.
  %With only a few particles in two-dimensions,
  %the simulation runs quickly,
  %making this an appropriate model for undergraduates to explore.  
\end{abstract}
% AJP requires an abstract for all regular article submissions.
% Abstracts are optional for submissions to the "Notes and Discussions" section.
